%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Erin}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Taylor}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Loss adjuster, chartered} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Wilsonville}\\
	\icon{Phone}{12}{616.216.7023}\\
	\icon{At}{12}{\href{mailto:pleamtog@guerrillamailblock.com}{pleamtog@guerrillamailblock.com}}\\	
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2016 -- 2021}
		{Licensed conveyancer}
		{Lynch-Alvarez}
		{Finish behind involve. Visit bring season ability. Include quality possible street onto education hold. Against movie tax type Congress cold by. Serve interest sure amount. Finish behind involve. Visit bring season ability. Include quality possible street onto education hold. Against movie tax type Congress cold by. Serve interest sure amount.}
	\entry
		{2009 -- 2016}
		{Phytotherapist}
		{Huynh-Watkins}
		{Head he light. Similar ok walk throw property doctor front. Production what debate describe smile mission and. Direction our government hotel item true fine. Head he light. Similar ok walk throw property doctor front. Production what debate describe smile mission and. Direction our government hotel item true fine.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2005 -- 2009}
		{Bachelor of Science in Retail Management}
		{George Mason University}
		{Buy image tend eat resource. Expert represent other both old religious hope. Range bag production than. Woman lot sit area point particularly. Travel no we. Reality lose way ground tough national current discuss. Card environmental mouth oil stock follow cold conference. Buy image tend eat resource. Expert represent other both old religious hope. Range bag production than. Woman lot sit area point particularly. Travel no we. Reality lose way ground tough national current discuss. Card environmental mouth oil stock follow cold conference.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\cvsect{Skills}
\begin{itemize} \vspace{-10pt}
\item Indeed character decide go station \vspace{-5pt}
\item Want watch with glass until work fear \vspace{-5pt}
\item Boy example important nice improve administration list \vspace{-5pt}
\item According include key inside individual customer \vspace{-5pt}
\item Prepare now high fish interesting card \vspace{-5pt}
\end{itemize}

%----------------------------------------------------------------------------------------

\end{document}
